Differences in the Risk of Grade Retention for Biracial and Monoracial Students in the US, 2010-2019

### 2022-12-07 products/paper/main.qmd
Use correct quarto code chunk headers in paper

```{r setup}
#| include: false
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
color_choices <- c("#003f5c","#58508d","#bc5090","#ff6361","#000000","#ffa600")
```

```{r load-data}
load(here("analysis","output","acs.RData"))
load(here("analysis","output","coef_table.RData"))
load(here("analysis","output","monoracial_results.RData"))
load(here("analysis","output","tbl_resources.RData"))
# change names of models for display
coef_table <- coef_table %>%
  mutate(model=factor(model,
                      levels=c("crude","fixed effects","cultural resources",
                               "parent resources"),
                      labels=c("Raw","Baseline model","Cultural model",
                               "Full model")))
ci_df <- ci_df %>%
  mutate(model=factor(model,
                      levels=c("crude","fixed effects","cultural resources",
                               "parent resources"),
                      labels=c("Raw","Baseline model","Cultural model",
                               "Full model")))
# create design object
acs_design <- acs %>%
  as_survey_design(ids = cluster, weights = perwt)
```

>>>>

```{r}
#: label: setup
#| include: false
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
color_choices <- c("#003f5c","#58508d","#bc5090","#ff6361","#000000","#ffa600")
```

```{r load-data}
#| label: load-data
#| include: false
load(here("analysis","output","acs.RData"))
load(here("analysis","output","coef_table.RData"))
load(here("analysis","output","monoracial_results.RData"))
load(here("analysis","output","tbl_resources.RData"))
# change names of models for display
coef_table <- coef_table %>%
  mutate(model=factor(model,
                      levels=c("crude","fixed effects","cultural resources",
                               "parent resources"),
                      labels=c("Raw","Baseline model","Cultural model",
                               "Full model")))
ci_df <- ci_df %>%
  mutate(model=factor(model,
                      levels=c("crude","fixed effects","cultural resources",
                               "parent resources"),
                      labels=c("Raw","Baseline model","Cultural model",
                               "Full model")))
# create design object
acs_design <- acs %>%
  as_survey_design(ids = cluster, weights = perwt)
```
